### 2020-03-04 submission/manuscript.Rmd
Use the term 'Snakemake workflow' instead of 'recipe'

| **Title**             | **Description**                                    |
| ----------------- | ---------------------------------------------- |
| base vs. ggplot   | Given input data and a figure, recreate the figure using R's base graphics or ggplot syntax   |
| Snakemake         | Given a bash script that contains an analysis pipeline, convert it to a series of recipes (can also be done with GNU Make) |
| DRYing code       | Given script with repeated code, create functions to remove repetition   |
| mothur and Vegan	| Given a pairwise community dissimilarity matrix, compare communities using the `adonis` function in the Vegan R package  |
| tidy data         | Given a wide-formatted data table, convert it to a long, tidy-formatted data table using tools from R's tidyverse  |
| GitFlow           | Participants file and claim an issue to add their name to a README file in a GitHub-hosted repository and file a pull request to complete the issue |
| Integrating R and google docs   | Scrape a google docs workbook and clean the data to identify previous Code Club presenters |

>>>>

| **Title**             | **Description**                                    |
| ----------------- | ---------------------------------------------- |
| base vs. ggplot   | Given input data and a figure, recreate the figure using R's base graphics or ggplot syntax   |
| Snakemake         | Given a bash script that contains an analysis pipeline, convert it to a Snakemake workflow (can also be done with GNU Make) |
| DRYing code       | Given script with repeated code, create functions to remove repetition   |
| mothur and Vegan	| Given a pairwise community dissimilarity matrix, compare communities using the `adonis` function in the Vegan R package  |
| tidy data         | Given a wide-formatted data table, convert it to a long, tidy-formatted data table using tools from R's tidyverse  |
| GitFlow           | Participants file and claim an issue to add their name to a README file in a GitHub-hosted repository and file a pull request to complete the issue |
| Integrating R and google docs   | Scrape a google docs workbook and clean the data to identify previous Code Club presenters |

### 2020-03-04 submission/manuscript.tex
Use the term 'Snakemake workflow' instead of 'recipe'

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.25\columnwidth}\raggedright
\textbf{Title}\strut
\end{minipage} & \begin{minipage}[b]{0.69\columnwidth}\raggedright
\textbf{Description}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.25\columnwidth}\raggedright
base vs.~ggplot\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given input data and a figure, recreate the figure using R's base
graphics or ggplot syntax\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Snakemake\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a bash script that contains an analysis pipeline, convert it to a
series of recipes (can also be done with GNU Make)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
DRYing code\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given script with repeated code, create functions to remove
repetition\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
mothur and Vegan\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a pairwise community dissimilarity matrix, compare communities
using the \texttt{adonis} function in the Vegan R package\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
tidy data\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a wide-formatted data table, convert it to a long, tidy-formatted
data table using tools from R's tidyverse\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
GitFlow\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Participants file and claim an issue to add their name to a README file
in a GitHub-hosted repository and file a pull request to complete the
issue\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Integrating R and google docs\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Scrape a google docs workbook and clean the data to identify previous
Code Club presenters\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.25\columnwidth}\raggedright
\textbf{Title}\strut
\end{minipage} & \begin{minipage}[b]{0.69\columnwidth}\raggedright
\textbf{Description}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.25\columnwidth}\raggedright
base vs.~ggplot\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given input data and a figure, recreate the figure using R's base
graphics or ggplot syntax\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Snakemake\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a bash script that contains an analysis pipeline, convert it to a
Snakemake workflow (can also be done with GNU Make)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
DRYing code\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given script with repeated code, create functions to remove
repetition\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
mothur and Vegan\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a pairwise community dissimilarity matrix, compare communities
using the \texttt{adonis} function in the Vegan R package\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
tidy data\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a wide-formatted data table, convert it to a long, tidy-formatted
data table using tools from R's tidyverse\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
GitFlow\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Participants file and claim an issue to add their name to a README file
in a GitHub-hosted repository and file a pull request to complete the
issue\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Integrating R and google docs\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Scrape a google docs workbook and clean the data to identify previous
Code Club presenters\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
